---
title: "Yahoo Finance API"
output: 
    rmarkdown::github_document:
        html_preview: true
---


## Introduction

Yahoo Finance offers a list of free APIs to provide various data for the financial markets and products in their [website](https://finance.yahoo.com/). The official specification of the APIs was never released. But recently, A website uses the name `yahoofinanceapi` as domain name and provide the API service with different subscription plan. They also provide their API specification from their [website](https://www.yahoofinanceapi.com/). Below shows their API specification JSON. 

<details>
<summary>Click to expend the specification JSON (very long)</summary>

```{json specification_json, code = xfun::read_utf8("./yahoo-finance-api-specification.json"), class.source = c("trim-bottom-margin")}
```

</details>

While they are charging the API service, the official Yahoo Finance offers free access to their API. We just need to switch the server url back to `https://query1.finance.yahoo.com` and use the same endpoint to obtain the desired data. Hence, with these specifications, this document aims to provide two functions to extract the OHLC and the price quotes from the API using both Python and R. 


## Extraction of OHLC Price

### Using Python 

```{python}
def getfromyahoo(symbol, interval, starttime, endtime, printUrl = False):
    """Extracting stock data from Yahoo Financa API
    
    Arguments:
        symbol      String     Stock symbol for Yahoo Finance. 
        
        interval    String     Data interval between two consective rows. 
                               Should be one of the following values:
                               ["1m", "2m", "5m", "10m", "15m", "30m",
                                "60m", "90m", "1h", "1d", "1wk", "1mo"].
                                
        startime    Integer    The epoch time indicating the starttime 
                               of the data.
        
        endtime     Integer    The epoch time indicating the endtime 
                               of the data.
    """
    import pandas as pd
    import numpy as np
    from functools import reduce
    import warnings, requests, json, sys, datetime
    
    starttime = int(starttime)
    endtime = int(endtime)
    
    baseurl = "https://query1.finance.yahoo.com/v8/finance/chart"
    url = "%s/%s?interval=%s&period1=%s&period2=%s" % (baseurl, symbol, interval, starttime, endtime)

    if printUrl: print(url)
    
    # GET response from API
    try:
        response = requests.get(url, timeout = 5, headers = {"User-Agent":""})
    except requests.exceptions.Timeout as e:
        warnings.warn('Timeout')
        print("Msg: " + str(e))
        return(None)
    except:
        e = sys.exc_info()[0]
        warnings.warn("Unknown error")
        print("Msg: " + str(e))
        return(None)
    
    
    if response != None:
        if response.status_code == 200:
            content = json.loads(response.content).get("chart").get("result")
            
            if len(content[0].get("indicators").get("quote")[0]) > 0:
                currency = np.nan if content[0].get("meta").get("currency") == None else content[0].get("meta").get("currency")
                
                timestamp = content[0].get("timestamp")
                
                quotes = content[0]["indicators"]["quote"][0]
                
                valid_cell = {key: set(i for i, x in enumerate(value) if x != None) for key, value in quotes.items()}
                valid_cell = list(reduce(set().union, valid_cell.values()))
                
                timestamp = {"datetime": [datetime.datetime.fromtimestamp(timestamp[i]) for i in valid_cell]}
                quotes = {key: [value[i] for i in valid_cell] for key, value in quotes.items()}
                
                outdf = pd.DataFrame.from_dict({**timestamp, **{"symbol": symbol}, **quotes, **{"currency": currency}})
                outdf = outdf[["datetime", "symbol", "open", "low", "high", "close", "volume", "currency"]]
                
                return(outdf)
                
            else: return(None)
        
        else:
            content = response.text
            msg = "\nsymbol: %s\nstatus: %s\ncontent: %s" % (symbol, response.status_code, content)
            warnings.warn(msg)
            return(None)

```

Below shows the result of the above function.

```{python}
from datetime import datetime
from datetime import timedelta
response = getfromyahoo(
    "AAPL", 
    "1h", 
    int((datetime.today() - timedelta(days = 1)).timestamp()), 
    int(datetime.today().timestamp())
)
```

```{r, echo = FALSE, class.output = c("trim-bottom-margin")}
knitr::kable(reticulate::py$response)
```

### Using R 

```{r}
getfromyahoo <- function(symbol, interval, starttime, endtime, printUrl = FALSE){
    # The symbol can be found in https://finance.yahoo.com/
    # Valid intervals are 1m, 2m, 5m, 15m, 30m, 60m, 90m, 1h, 1d, 5d, 1wk, 1mo, 3mo
    # Starttime and endtime are in epoch format and should be in integer form correct to the nearest second
    
    starttime <- as.integer(as.numeric(starttime))
    endtime <- as.integer(as.numeric(endtime))
    
    baseurl <- "https://query1.finance.yahoo.com/v8/finance/chart"
    url <- sprintf("%s/%s?interval=%s&period1=%s&period2=%s", baseurl, symbol, interval, starttime, endtime)
    
    if (printUrl) print(url)
    
    # GET response from API
    response <- tryCatch(
        expr = httr::GET(url, httr::timeout(5)), 
        error = function(e) if (substr(e$message, 1, 7) == "Timeout") {
            return(list(status = "Timeout", error = e))
        } else {
            return(list(status = "Unknown error", error = e))
        }
    )
    
    if (class(response) == "response"){
        # Check the status
        if (response$status_code == 200){
            content <- httr::content(response)$chart$result
            
            # Double check if the content contains the quotes
            if (length(content[[1]]$indicators$quote[[1]]) > 0){
                currency <- ifelse(is.null(content[[1]]$meta$currency), NA, content[[1]]$meta$currency)
                
                # Extract the timestamp
                timestamp <- content[[1]]$timestamp
                
                # Extract the quotes
                eval(parse(text = sprintf("%1$s <- content[[1]]$indicators$quote[[1]]$%1$s", c("open", "low", "high", "close", "volume"))))
                
                # There are some nulls in the quotes. Identify the valid cells
                eval(parse(text = sprintf("%1$s.valid <- which(!sapply(%1$s, is.null))", c("open", "low", "high", "close", "volume"))))
                
                valid_cell <- Reduce(union, list(open.valid, low.valid, high.valid, close.valid, volume.valid))
                
                # Remove the entire rows if every quotes in those rows are nulls
                eval(parse(text = sprintf("%1$s <- unlist(%1$s[valid_cell])", c("timestamp", "open", "low", "high", "close", "volume"))))
                
                # Create the dataframe
                outdf <- data.frame(datetime = as.POSIXct(timestamp, origin = "1970-01-01"),
                                    symbol = symbol,
                                    open = open, 
                                    low = low, 
                                    high = high, 
                                    close = close,
                                    volume = volume,
                                    currency = currency)
                return(outdf)
            } else return(NA)
        } else {
            content <- httr::content(response)
            msg <- sprintf("\nsymbol: %s\nstatus: %s\ncontent: %s", symbol, response$status_code, content)
            warning(msg)
            return(NA)
        }
    } else {
        msg <- sprintf("\nsymbol: %s\nstatus: %s\nerror: %s", symbol, response$status, response$error)
        warning(msg)
        return(NA)
    }
}
```

Below shows the result of the above function.

```{r}
response <- getfromyahoo("AAPL", "1h", Sys.time() - 24*60*60, Sys.time())
```

```{r, echo = FALSE, class.output = c("trim-bottom-margin")}
knitr::kable(response)
```


## Extraction of Price Quote

### Using Python 

```{python}
def yahooQuotes(symbols):
    import requests
    import json
    import pandas as pd
    if isinstance(symbols, list): symbol = ",".join(symbols)
    if isinstance(symbols, str): symbol = symbols
    url = "https://query1.finance.yahoo.com/v6/finance/quote?symbols=" + symbol
    response = requests.get(url, headers = {"User-Agent":""})
    if response.ok:
        content = json.loads(response.content)
        result = content["quoteResponse"]["result"]
        if len(result) > 0:
            if len(result) == 1: return(result[0])
            result = pd.DataFrame(result)
            return(result)
    else:
        return(None)
```

Below shows the result of the above function.

```{python}
response = yahooQuotes(["0001.HK", "AAPL"])
```

```{r, echo = FALSE}
knitr::kable(reticulate::py$response)
```

### Using R

```{r}
yahooQuotes <- function(symbols) {
    symbol <- paste0(symbols, collapse = ",")
    url <- paste0("https://query1.finance.yahoo.com/v6/finance/quote?symbols=", symbol)
    response <- httr::GET(url)
    if (response$status_code == 200) {
        content <- httr::content(response)
        if (length(content$quoteResponse$result) > 0){
        if (length(content$quoteResponse$result) == 1) result <- content$quoteResponse$result[[1]]
        result <- plyr::rbind.fill(lapply(content$quoteResponse$result, as.data.frame))
        if (length(symbols) > length(result$symbol)) {
            missingSymbols <- setdiff(symbols, result$symbol)
            warning(sprintf("The following symbol(s) are missing from the result: %s", paste(missingSymbols, collapse = ", ")))
        }
        return(result)
        } else {
        warning("No result found, returning NA")
        return(NA)
        }
    }
}
```

Below shows the result of the above function.

```{r}
knitr::kable(yahooQuotes(c("0001.HK", "AAPL")))
```

